An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2013-02-04 Paper.tex
Edit Lemma A.1
Tweaks proof and adds additional conditions.

\begin{thm}\label{res:3}
  Suppose the following conditions hold:
  \begin{enumerate}
  \item Let $\{y_t, z_t\}$ be an $L_2$-\textsl{\ned} process of size $-\frac12$ on
    a strong mixing series $\{V_t\}$ of size $-\frac{r}{r-2}$, with $r
    > 2$.
  \item The estimator $\hat{\beta}_t$ of $\beta_0$ is estimated with a
    recursive, rolling, or fixed estimation window and satisfies
    $\hat{\beta}_{t} - \beta_{0} = \hat{B}_{t} H_t$; $\hat{B}_{t}$ is
    a sequence of $k$ by $q$ matrices such that $\sup_t |\hat{B}_t -
    B| \to^p 0$, $\sup_t |\hat{B}_t^{*} - B^{*}| \to^p 0$, and $B^{*}
    = B + o_p$; $H_{t}$ is a sequence of $q$-vectors such that 
    \begin{equation}
      H_{t} = \begin{cases} 
        \tfrac1t \sum_{s=1}^t h_{s} & \text{recursive window} \\
        \tfrac1R \sum_{s=t-R+1}^t h_{s} & \text{rolling window} \\
        \tfrac1R \sum_{s=1}^R h_{s} & \text{fixed window} \\
      \end{cases}
    \end{equation}
    $h_{s}(\beta) = h(y_{s}, z_{s}, \beta)$, $h_s = h_s(\beta_0)$, and
    $\E h_{s} = 0$ for all $s$.
  \item Let $f_{t}(\beta) = f(y_{t}, z_{t}, \beta)$ be an $l$-vector;
    $\| \sup_{\beta \in N} f_{t}(\beta) \|_{r+\delta}$ and $\|
    \sup_{\beta \in N} h_{t}(\beta) \|_{r+\delta}$ are uniformly
    finite in $t$, where $N$ is an open neighborhood of $\beta_{0}$.
  \item Each element of $\E f_{t}(\beta)$ is continuously
    differentiable in the neighborhood $N$.  Moreover, $\sup_{\beta
      \in N} | F_{t}(\beta) |$ is uniformly finite in $t$ with
    $F_{t}(\beta) = \dd{\beta'} \E f_{t}(\beta)$.
  \item There exist finite constants $C$, $\phi > 0$, and $Q \geq r$
    such that \[\sup_{\epsilon : N(\beta_{0}, \epsilon) \subset N}\|
    \sup_{\beta \in N(\beta_{0}, \epsilon)} f_{t}(\beta) - f_{t} \|_Q
    \leq C \epsilon^{\phi}\] and \[\sup_{\epsilon : N(\beta_{0},
      \epsilon) \subset N}\| \sup_{\beta \in N(\beta_{0}, \epsilon)}
    h_{t}(\beta) - h_{t} \|_Q \leq C \epsilon^{\phi},\] where
    $N(\beta, \epsilon) = \{b : |b - \beta| < \epsilon\}$.
  \item $R, P \to \infty$ as $T \to \infty$.
  \item $X_1^{*},\dots,X_T^{*}$ are generated by the moving blocks,
    circular blocks, or stationary bootstrap with block lengths drawn
    from the geometric distribution, and $b$ satisfies $b \to \infty$
    and $\frac{b}{P} \to 0$; $b$ is the block length of the moving or
    circular blocks bootstraps and is the expected block length of the
    stationary bootstrap.
  \item The asymptotic variance matrix of $\bar{f}(\beta_0)$ is
    uniformly positive definite and $\E f_t(\beta_0) = \E
    f_s(\beta_0)$ for all $s$ and $t$.
  \end{enumerate}
  Then
  \begin{equation}
    \pr[\sup_x | \pr^*[\sqrt{P} (\bar{f}^* - \bar{f}(\hat{\beta}_{T+1}))
        \leq x] - \pr[\sqrt{P}( \bar{f} - \E \bar{f}(\beta_0)) \leq x] | >
      \epsilon] \to 0
  \end{equation}
  for all $\epsilon > 0$.
\end{thm}

@@

\begin{lema}\label{res:a2}
  Suppose $a \in [0,\frac12)$ and the conditions of Theorem~\ref{res:3}
  hold.
  \begin{enumerate}
  \item $P^a \sup_t | H_{t} | \to^p 0$ and $P^a \sup_t | H_{t}^{*} |
    \to^{p^{*}} 0$.
  \item $P^a \sup_t | \hat{\beta}_{t} - \beta_{0} | \to^{p} 0$ and
    $P^a \sup_t | \hat{\beta}^{*}_{t} - \hat{\beta}_{T+1} |
    \to^{p^{*}} 0$.
  \end{enumerate}
\end{lema}

\begin{proof}[Proof of Lemma~\ref{res:a2}] \quad
  \begin{enumerate}
  \item The process $\tfrac{1}{\sqrt{T}} h_{s}$ satisfies \citepos[Theorem
    3.1]{JoD:00b} functional \clt.  So
    \begin{equation}
      P^a \sup_t \Big| \tfrac1t \sum_{s=1}^t h_{s} \Big| =
      P^a \sup_{\gamma \in [0,1]} \Big| \tfrac{1}{\lfloor \gamma
        T\rfloor} \sum_{s=1}^{\lfloor \gamma T \rfloor} h_{s} \Big| \to^{p} 0
    \end{equation}
    with the convergence following from the continuous mapping
    theorem.  \citepos{Cal:11d} Theorem~1 ensures the same argument
    holds for $\tfrac{1}{\sqrt{T}} h_s^{*}$.
  \item We have
    \begin{multline}
      P^a \sup_{t \in S_T} | \hat{\beta}_t - \beta_0 | = P^a \sup_{t
        \in S_T} |\hat{B}_{t} H_{t}| \\ \leq \sup_{t,u \in S_T} \Big|
      [ \hat{B}_u - B] \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big| + \sup_{t\in S_T} \Big|
      B \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big|
    \end{multline}
    and both terms converge to zero in (conditional) probability by
    the previous argument and by assumption.  The same argument holds
    for $\hat{\beta}_t^{*} - \hat{\beta}_{T+1}$ as well.
  \end{enumerate}
\end{proof}

>>>>

\begin{thm}\label{res:3}
  Suppose the following conditions hold:
  \begin{enumerate}
  \item Let $\{y_t, z_t\}$ be an $L_2$-\textsl{\ned} process of size $-\frac12$ on
    a strong mixing series $\{V_t\}$ of size $-\frac{r}{r-2}$, with $r
    > 2$.
  \item The sequence $(y_1^{*}, z_t^*),\dots,(y_T^{*}, z_T^*)$ is
    generated by the moving blocks, circular blocks, or stationary
    bootstrap with block lengths drawn from the geometric
    distribution, and $b$ satisfies $b \to \infty$ and $\frac{b}{P}
    \to 0$; $b$ is the block length of the moving or circular blocks
    bootstraps and is the expected block length of the stationary
    bootstrap.
  \item The estimator $\hat{\beta}_t$ of $\beta_0$ is estimated with a
    recursive, rolling, or fixed estimation window and satisfies
    $\hat{\beta}_{t} - \beta_{0} = \hat{B}_{t} H_t$; $\hat{B}_{t}$ is
    a sequence of $k$ by $q$ matrices such that $\sup_t |\hat{B}_t -
    B| \to^p 0$, $\sup_t |\hat{B}_t^{*} - B^{*}| \to^p 0$, and $B^{*}
    = B + o_p$; $H_{t}$ is a sequence of $q$-vectors such that 
    \begin{equation}
      H_{t} = \begin{cases} 
        \tfrac1t \sum_{s=1}^t h_{s} & \text{recursive window} \\
        \tfrac1R \sum_{s=t-R+1}^t h_{s} & \text{rolling window} \\
        \tfrac1R \sum_{s=1}^R h_{s} & \text{fixed window} \\
      \end{cases}
    \end{equation}
    $h_{s}(\beta) = h(y_{s}, z_{s}, \beta)$, $h_s = h_s(\beta_0)$, and
    $\E h_{s} = 0$ for all $s$; and $\frac12 \sum_{t=1}^T h_t^* = 0$
    a.s. where $h_t^* = h(y_s^*, z_s^*, \hat\beta_T)$.  Also define
    \begin{equation}
      H_{t}^* = \begin{cases} 
        \tfrac1t \sum_{s=1}^t h_{s}^* & \text{recursive window} \\
        \tfrac1R \sum_{s=t-R+1}^t h_{s}^* & \text{rolling window} \\
        \tfrac1R \sum_{s=1}^R h_{s}^* & \text{fixed window} \\
      \end{cases}
    \end{equation}
  \item Let $f_{t}(\beta) = f(y_{t}, z_{t}, \beta)$ be an $l$-vector;
    $\| \sup_{\beta \in N} f_{t}(\beta) \|_{r+\delta}$ and $\|
    \sup_{\beta \in N} h_{t}(\beta) \|_{r+\delta}$ are uniformly
    finite in $t$, where $N$ is an open neighborhood of $\beta_{0}$.
  \item Each element of $\E f_{t}(\beta)$ is continuously
    differentiable in the neighborhood $N$.  Moreover, $\sup_{\beta
      \in N} | F_{t}(\beta) |$ is uniformly finite in $t$ with
    $F_{t}(\beta) = \dd{\beta'} \E f_{t}(\beta)$.
  \item There exist finite constants $C$, $\phi > 0$, and $Q \geq r$
    such that \[\sup_{\epsilon : N(\beta_{0}, \epsilon) \subset N}\|
    \sup_{\beta \in N(\beta_{0}, \epsilon)} f_{t}(\beta) - f_{t} \|_Q
    \leq C \epsilon^{\phi}\] and \[\sup_{\epsilon : N(\beta_{0},
      \epsilon) \subset N}\| \sup_{\beta \in N(\beta_{0}, \epsilon)}
    h_{t}(\beta) - h_{t} \|_Q \leq C \epsilon^{\phi},\] where
    $N(\beta, \epsilon) = \{b : |b - \beta| < \epsilon\}$.
  \item $R, P \to \infty$ as $T \to \infty$.
  \item The asymptotic variance matrix of $\bar{f}(\beta_0)$ is
    uniformly positive definite and $\E f_t(\beta_0) = \E
    f_s(\beta_0)$ for all $s$ and $t$.
  \end{enumerate}
  Then
  \begin{equation}
    \pr[\sup_x | \pr^*[\sqrt{P} (\bar{f}^* - \bar{f}(\hat{\beta}_{T}))
        \leq x] - \pr[\sqrt{P}( \bar{f} - \E \bar{f}(\beta_0)) \leq x] | >
      \epsilon] \to 0
  \end{equation}
  for all $\epsilon > 0$.
\end{thm}

@@

\begin{lema}\label{res:a2}
  Suppose $a \in [0,\frac12)$ and the conditions of Theorem~\ref{res:3}
  hold.
  \begin{enumerate}
  \item $P^a \sup_t | H_{t} | \to^p 0$ and $P^a \sup_t | H_{t}^{*} |
    \to^{p^{*}} 0$.
  \item $P^a \sup_t | \hat{\beta}_{t} - \beta_{0} | \to^{p} 0$ and
    $P^a \sup_t | \hat{\beta}^{*}_{t} - \hat{\beta}_T |
    \to^{p^{*}} 0$.
  \end{enumerate}
\end{lema}

\begin{proof}[Proof of Lemma~\ref{res:a2}] \quad
  \begin{enumerate}
  \item The process $\tfrac{1}{\sqrt{T}} h_{s}$ satisfies \citepos[Theorem
    3.1]{JoD:00b} functional \clt.  So
    \begin{equation}
      P^a \sup_t \Big| \tfrac1t \sum_{s=1}^t h_{s} \Big| =
      P^a \sup_{\gamma \in [0,1]} \Big| \tfrac{1}{\lfloor \gamma
        T\rfloor} \sum_{s=1}^{\lfloor \gamma T \rfloor} h_{s} \Big| \to^{p} 0
    \end{equation}
    with the convergence following from the continuous mapping
    theorem.  \citepos{Cal:11d} Theorem~2 ensures the same argument
    holds for $\tfrac{1}{\sqrt{T}} h_s^{*}$.
  \item We have
    \begin{multline}
      P^a \sup_t | \hat{\beta}_t - \beta_0 | = P^a \sup_t |\hat{B}_{t}
      H_{t}| \\ \leq \sup_{t,u \in S_T} \Big| [ \hat{B}_u - B]
      \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big| + \sup_{t\in S_T} \Big|
      B \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big|
    \end{multline}
    and both terms converge to zero in (conditional) probability by
    the previous argument and by assumption.  The same argument holds
    for $\hat{\beta}_t^{*} - \hat{\beta}_{T+1}$ as well.
  \end{enumerate}
\end{proof}
